\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{lipsum} % for placeholder text, remove if not needed

\title{IBM AI AR techdoc}
\author{Ani Bitri}

\begin{document}

\maketitle

\tableofcontents
\newpage

\section{Introduction}
This document provides a detailed specification for the proposed software project. It outlines the goals, requirements, and constraints that are necessary for successful implementation.

\section{Project Overview}
\subsection{Purpose}
Many developers face challenges while reading and understanding technical documentation. This project aims to create an AI-powered mobile application which, supported by AR technology, will enhance the user experience
by providing interactive and immersive documentation. Powered by IBM Watson/Grantie, the app will offer several features to assist developers in navigating and comprehending complex technical documents, including text recognition,
interactive AR overlays, chatbot assistance and more.

\subsection{Objectives within the scope}

\subsection{Boundaries and Out-of-Scope Elements}

\subsection{Expected Deliverables}

\subsection{Target Outcomes}

\section{Literature Review}


\section{Requirements}
\subsection{Functional Requirements}
List the key functionalities the software system must support. Provide clear and concise descriptions of features and interactions.

\subsection{Non-Functional Requirements}
Outline performance, usability, reliability, and other quality attributes expected from the system.

\section{System Architecture}
Provide a high-level overview of the system architecture. Include diagrams where appropriate to illustrate the system components and their interactions.

\section{Frontend Design}

\section{Backend Design}

\subsection{Component Diagram}
\begin{center}
% Insert component diagram here
\end{center}

\subsection{Technology Stack}
List the technologies, programming languages, frameworks, and tools that will be used in the project.

\section{Development Plan}
\subsection{Milestones}
Detail the project timeline with key milestones and deliverables.

\subsection{Risk Management}
Identify potential risks and outline strategies for mitigating them.

\section{Conclusion}
Summarize the key points of the specification document and outline next steps.

\end{document}